Testing Gravity using Type Ia Supernovae Discovered by LSST

### 2018-12-13 doc/article.tex
forging on

\section{Important Elements in Designing a Supernova Survey to Measure $\MakeLowercase{f}\sigma_8$}
\citet{2017ApJ...847..128H} perform their analysis in Fourier space, 
where the Fisher information matrix of a random Gaussian field with mean zero and covariance $C(k)$ parameterized by $\lambda$ is
\begin{equation}
F_{ij} = \frac{V}{2}\int \frac{d^3k}{(2\pi)^3} \text{Tr}\left[ C^{-1} \frac{\partial C}{\partial \lambda_i} C^{-1}
\frac{\partial C}{\partial \lambda_j} \right],
\end{equation}
where the covariance for the velocity-velocity correlation
\begin{equation}
C = P_{vv}(k) + \frac{\sigma^2}{n}
\label{cov:eq}
\end{equation}
is dependent on the power spectrum, noise in the velocity measurement, and the density of velocity probes
\citep{2017MNRAS.464.2517H}.

The precision in the determination of the combination $\lambda= f\sigma_8$ is estimated using the Fisher matrix.  To first order, 
$P_{vv} \propto (f\sigma_8)^2$.

The survey parameters that determine parameter precision are the volume $V$, which
in turn can be parameterized by the survey solid angle $\Omega$ and the redshift depth $z_{max}$ ; the number density of sources $n$; and the intrinsic
magnitude dispersion $\sigma_M$, where magnitude and velocity dispersions are related by $\sigma_{M} = \frac{5}{\ln{10}} \frac{1+z}{z} \sigma$.
For surveys of fixed depth, the variance of $f\sigma_8$ 
in the sample-variance limit  
is inversely proportional to the survey solid-angle $\Omega$, whereas
in the shot-noise limit the variance is inversely proportional to $\Omega n^2 \propto N^2/\Omega$, where $n$ is the number density,
and $N$ is the total number of supernovae.

LSST is expected to discover all $z<0.3$ SNe~Ia before maximum light in its active Wide Fast Deep (WFD) survey area.
Equating LSST discovery with having a meaningful peculiar velocity, $n$ is thus a non-tunable parameter.  This leaves
solid angle, redshift depth, and intrinsic magnitude dispersion as the important tunable parameters in the design of a peculiar velocity survey.

>>>>

\section{Important Elements in Designing a Supernova Survey to Measure $\MakeLowercase{f}\sigma_8$}
\citet{2017ApJ...847..128H} perform their analysis in Fourier space, 
where the Fisher information matrix of a random Gaussian field with mean zero and covariance $C(k)$ parameterized by $\lambda$ is
\begin{equation}
F_{ij} = \frac{V}{2}\int \frac{d^3k}{(2\pi)^3} \text{Tr}\left[ C^{-1} \frac{\partial C}{\partial \lambda_i} C^{-1}
\frac{\partial C}{\partial \lambda_j} \right],
\end{equation}
where the covariance for the velocity-velocity correlation
\begin{equation}
C = P_{vv}(k) + \frac{\sigma^2}{n}
\label{cov:eq}
\end{equation}
is dependent on the power spectrum, noise in the velocity measurement, and the density of velocity probes
\citep{2017MNRAS.464.2517H}.  
The primary dependence on the growth of structure is through
\begin{equation}
\frac{\partial C}{\partial \lambda} = \frac{\partial P_{vv}}{\partial \lambda} = \text{constant}
\end{equation}
for the parameter choice
$\lambda=(f\sigma_8)^2$.  In the sample-variance limit, $F_{\lambda \lambda} \propto V$ whereas in the shot noise limit $F_{\lambda \lambda} \propto V n^2 \sigma^{-4}$.

The survey parameters that determine parameter precision are the volume $V$, which
in turn can be parameterized by the survey solid angle $\Omega$ and the redshift depth $z_{max}$ ; the number density of sources $n$; and the intrinsic
magnitude dispersion $\sigma_M$, where magnitude and velocity dispersions are related by $\sigma_{M} = \frac{5}{\ln{10}} \frac{1+z}{z} \sigma$.
LSST is expected to discover all $z<0.3$ SNe~Ia before maximum light in its active Wide Fast Deep (WFD) survey area.
Equating LSST discovery with having a meaningful peculiar velocity, $n$ is thus a non-tunable parameter.

For surveys of fixed depth, the variance of $f\sigma_8$ 
in the sample-variance limit  
is inversely proportional to the survey solid-angle $\Omega$, whereas
in the shot-noise limit the variance is inversely proportional to $\Omega n^2 \propto N^2/\Omega$, where $n$ is the number density,
and $N$ is the total number of supernovae.
